\section{Contributions}

We describe the work we have done, jointly and individually.

Elnikety: Eslam helped define the problem.
He read related work in trusted computing, trying to pin down which capabilities a system can provide when integrated with a secure cryptocard.
He helped write our project proposal.
Later, during the implementation, he worked on the cryptocard DAA code.
He wrote~\secref{impl} of this report and contributed to the rest.

Kapcari: Edit helped define the problem.
She investigated the available capabilities for TPM on Linux machines.
She presented our proposal to the class.
During the implementation, she worked on the network communication between the issuer, the cryptocard, and the verifier.

Rajani: Vineet helped define the problem.
During the implementation, he investigated access to the cryptocard and how to compile, deploy, and communicate with custom-built binary images on the cryptocard.
He worked on the cryptocard DAA code.
He contributed to this report.

Swasey: David helped define the problem.
He read related work on trusted computing, IBM cryptocards, and zero-knowledge proofs.
He was primary author on the project proposal.
He closely read the DAA paper and related literature and explained them to the group.
He implemented the full DAA protocol in ML.
He wrote Sections~\ref{sec:daa}--\ref{sec:background} of this report and contributed to the rest.

\if 0

\begin{comment}
	\emph{EE:} Aniket’s Summary of Contributions (no hosing)
\end{comment}

Elnikety
- Defining the problem
- Writing the proposal
- The cryptocard prover code
- Writing the experience report

Kapcari:
- Defining the problem
- Presenting the proposal
- Network communication between the prover and verifier

Rajani:
- Defining the problem
- Early efforts in understanding how to deploy a program into the secure
cryptocard
- The cryptocard prover code 

Swasey:
- Defining the problem
- Writing the proposal
- Going through the literature to pin down the exact algorithms to be used in
the implementation
- Full prover/verifier code in ML
- Writing the experience report

\fi